---
title: "p8105_hw3_kx2173"
author: "ke"
output: github_document
---

```{r}
library(tidyverse)
```


## Problem 1

Load tha data from package.
```{r}
library(p8105.datasets)
data("instacart")
```

This data set has `r ncol(instacart)` columns and `r nrow(instacart)` rows, with `r ncol(instacart)` variables including `r names(instacart)`.


```{r}
instacart %>% 
  janitor::clean_names() 
```


#### How many aisles are there, and which aisles are the most items ordered from?
```{r}
instacart %>% 
  group_by(aisle) %>% 
  summarize(n_obs = n()) %>% 
  arrange(desc(n_obs))
```
There are 134 aisles, and the item "fresh vegetables" is the most item ordered from.


#### Make a plot that shows the number of items ordered in each aisle, limiting this to aisles with more than 10000 items ordered. Arrange aisles sensibly, and organize your plot so others can read it.
```{r}
instacart %>% 
  group_by(aisle) %>% 
  summarize(n_obs = n()) %>% 
  filter(n_obs > 10000) %>% 
  mutate(aisle = fct_reorder(aisle, n_obs)) %>% 
  ggplot(aes(x = n_obs, y = aisle)) + 
  geom_col(width = .5,
           position = position_dodge(width = 1)) +
  labs(title = "Number of items ordered in each aisle",
       subtitle = "with aisles more than 10,000 ordered items",
       x = "Number of items ordered",
       y = "Category of aisle"
       )
```


#### Make a table showing the three most popular items in each of the aisles “baking ingredients”, “dog food care”, and “packaged vegetables fruits”. Include the number of times each item is ordered in your table.
```{r}
baking_ingredients = instacart %>% 
  filter(aisle == "baking ingredients") %>% 
  group_by(product_name) %>% 
  summarize(n_obs = n()) %>% 
  arrange(desc(n_obs)) %>% 
  head(3)

dog_food_care = instacart %>% 
  filter(aisle == "dog food care") %>% 
  group_by(product_name) %>% 
  summarize(n_obs = n()) %>% 
  arrange(desc(n_obs)) %>% 
  head(3)

packaged_vegetables_fruits = instacart %>% 
  filter(aisle == "packaged vegetables fruits") %>% 
  group_by(product_name) %>% 
  summarize(n_obs = n()) %>% 
  arrange(desc(n_obs)) %>% 
  head(3)

table_three = 
  bind_rows(baking_ingredients, dog_food_care, packaged_vegetables_fruits) 

knitr::kable(table_three)
```


#### Make a table showing the mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered on each day of the week; format this table for human readers.
```{r}
mean_hr_of_two = instacart %>% 
  filter(product_name %in% c("Pink Lady Apples", "Coffee Ice Cream")) %>%
  group_by(product_name, order_dow) %>% 
  summarise(mean_hr = 
            round(mean(order_hour_of_day, na.rm = TRUE),digits = 1), 
            .groups = "drop") %>% 
  mutate(order_dow = recode(order_dow,
                            `1` = "Monday",
                            `2` = "Tuesday",
                            `3` = "Wednesday",
                            `4` = "Thursday",
                            `5` = "Friday",
                            `6` = "Saturday",
                            `0` = "Sunday")) %>% 
  pivot_wider(
    names_from = "order_dow",
    values_from = "mean_hr"
  )

knitr::kable(mean_hr_of_two,
             caption = "Mean hour of the day for which Pink Lady Apples and Coffee Ice Cream are ordered")
```


## Problem 2


Load data from package.
```{r}
library(p8105.datasets)
data("brfss_smart2010")
```

#### Do some data cleaning.
```{r}
brfss_clean = brfss_smart2010 %>% 
  janitor::clean_names() %>% 
  filter(topic == "Overall Health",
         response %in% c("Excellent", "Very good", "Good", "Fair", "Poor")) %>% 
  mutate(response = 
           fct_relevel(response, 
                       c("Excellent", "Very good", "Good", "Fair", "Poor"))) %>%
  arrange(desc(response))
```


#### In 2002, which states were observed at 7 or more locations? What about in 2010?
```{r}
location_2002 = brfss_clean %>% 
  filter(year == "2002") %>% 
  select(year:locationdesc) %>% 
  distinct() %>% 
  group_by(locationabbr) %>% 
  summarize(n_obs = n()) %>% 
  filter(n_obs >= 7) %>% 
  arrange(desc(n_obs))

location_2010 = brfss_clean %>% 
  filter(year == "2010") %>% 
  select(year:locationdesc) %>% 
  distinct() %>% 
  group_by(locationabbr) %>% 
  summarize(n_obs = n()) %>% 
  filter(n_obs > 7) %>% 
  arrange(desc(n_obs))
```
##### In 2002, there are 6 states (PA, MA, NJ, CT, FL, NC) observed at 7 or more locations, and in 2010, there are 11 states (FL, NJ, TX, CA, MD, NC, NE, WA, MA, NY, OH) observed at 7 or more locations.


#### Construct a dataset that is limited to Excellent responses, and contains, year, state, and a variable that averages the data_value across locations within a state. Make a “spaghetti” plot of this average value over time within a state
```{r, fig.width = 6, fig.height = 12}
brfss_clean %>% 
  filter(response == "Excellent") %>% 
  select(year, locationabbr, data_value) %>% 
  group_by(year, locationabbr) %>% 
  summarise(mean_data_value = round(mean(data_value, na.rm = TRUE), digits = 2), 
            .groups = "drop") %>% 
  ggplot(aes(x = year, y = mean_data_value, color = locationabbr)) +
  geom_line() +
  labs(
    title = "Mean data value for states, limiting to Excellent reponses",
    x = "Year",
    y = "Mean data value",
  )
```


#### Make a two-panel plot showing, for the years 2006, and 2010, distribution of data_value for responses (“Poor” to “Excellent”) among locations in NY State.
```{r}
brfss_clean %>% 
  filter(year %in% c(2006, 2010),
         locationabbr == "NY") %>%
  select(year, locationabbr, response, data_value) %>% 
  mutate(year = as.character(year)) %>% 
  ggplot(aes(x = data_value, color = year)) +
  geom_density() +
  facet_grid(. ~year) +
  labs(
    title = "Distribution of data value for 2006 & 2010 in NY",
    x = "Data value for responses",
    y = "Density of data value",
  ) +
  theme(plot.title = element_text(hjust = .4))
```


## Problem 3


#### Load, tidy, and otherwise wrangle the data. 
```{r}
accel_df = read_csv("data_problem3/accel_data.csv")

accel_clean = accel_df %>% 
  janitor::clean_names() %>% 
  mutate(
    weekday_weekend = case_when(
    day == "Monday" ~ "Weekday",
    day == "Tuesday" ~ "Weekday",
    day == "Wednesday" ~ "Weekday",
    day == "Thursday" ~ "Weekday",
    day == "Friday" ~ "Weekday",
    day == "Saturday" ~ "Weekend",
    day == "Sunday" ~ "Weekend",
  ),
  day = as.factor(day),
  day = fct_relevel(day,
                    c("Monday", "Tuesday", "Wednesday", "Thursday", 
                      "Friday", "Saturday", "Sunday"))) %>% 
  relocate(week, day_id, day, weekday_weekend) %>% 
  pivot_longer(
    activity_1:activity_1440,
    names_to = "activity_min",
    names_prefix = "activity_",
    values_to = "activity_counts"
  ) %>% 
  mutate(
    activity_min = as.numeric(activity_min),
    weekday_weekend = as.factor(weekday_weekend)
    )
  
```

Describe the resulting dataset:
This data set has `r ncol(accel_clean)` variables and `r nrow(accel_clean)` observations.
Variables are `r names(accel_clean)`.
Here are variable descriptions:
`r colnames(accel_clean)[1]`: Number of week.
`r colnames(accel_clean)[2]`: Number of day.
`r colnames(accel_clean)[3]`: the day that related to `r colnames(accel_clean)[2]`.
`r colnames(accel_clean)[4]`: Whether it is a weekday or weekend.
`r colnames(accel_clean)[5]`: Each activity minute.
`r colnames(accel_clean)[6]`: The counts on each activity minute.


























